gradient_analysis

### 2021-01-25 gradient_analysis.Rmd
clean up scripts

---
title: "gradient_analysis"
author: "Daniel Suh"
date: "10/30/2020"
output: html_document
---

>>>>

---
title: "gradient_analysis"
author: "Daniel Suh"
date: "10/30/2020"
output: html_document
---
I used this document as my instructions for most of this analysis. https://sites.ualberta.ca/~lkgray/uploads/7/3/6/2/7362679/07-gradientanalysis.pdf s
